\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
Added photos of the L2TOR setup
WIP design architecture

\subsection{Situation Assessment}

@@

\subsection{A layered model of the environment}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{overview}
    \caption{Schema of a \uwds network: eight possible, user-written
    \emph{clients} (in blue) are exchanging environment models through four shared
    \emph{worlds} (made of joint spatial and temporal models). This architecture
    enables successive and modular refinement of the models
    (\emph{cascading} situation assessment), effectively adapted to each
    client's needs (yellow nodes represent other possible components in the system that do not
interact directly with the \uwds network).} \label{fig|scene} \end{figure}

(worlds are effectively composed of a scene graph representing the 3D geometry
of the environment, and a timeline storing temporal events)

@@

Figure~\ref{fig|scene} pictures a typically \uwds topology.

\subsection{Worlds}
\subsubsection{Scenes}

@@

\subsection{Standard Clients}

@@

\section{Applications}

@@

>>>>

\subsection{Cascading Situation Assessment}

@@

Figure~\ref{fig|scene} pictures a typically \uwds topology: a graph (that
happens to be a directed acyclic graph on Figure~\ref{fig|scene}, but does not
have to be in the general case -- cycles are permitted) of \emph{clients}
connected through shared data structures called \emph{worlds}.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{overview}
    \caption{Schema of a \uwds network: eight possible, user-written
    \emph{clients} (in blue) are exchanging environment models through four shared
    \emph{worlds} (made of joint spatial and temporal models). This architecture
    enables successive and modular refinement of the models
    (\emph{cascading} situation assessment), effectively adapted to each
    client's needs (yellow nodes represent other possible components in the system that do not
    interact directly with the \uwds network).}

    \label{fig|scene}

\end{figure}

\subsubsection{Clients}

Software components accessing \uwds worlds are called clients. Some standard
clients (like a 3D visualization tool) are provided with the \uwds package (see
section~\ref{std_clients}), but clients are otherwise written by the end users
using the \uwds client API (see section~\ref{api}).

Clients can both read and write onto the worlds they are connected to, and
automatically see updates broadcasted by other clients connected to the same
worlds.

Four specific types of clients can be distinguished: \textbf{root clients} which
create and update worlds (`write-only' client, like the \emph{Sensor fusion} and
\emph{ROS interface} clients on Figure~\ref{fig|scene}); \textbf{leaf clients}
which on the contrary only read worlds, without modifying them (like the
\emph{Computation of spatial relations} client on Figure~\ref{fig|scene});
\textbf{filters} that copy an input world into an output world, performing
some filtering operation in-between (like the client \textit{Physics-based
position correction}); and \textbf{transformers} which transform one
representation into another (like the \emph{Semantic mapping} client on
Figure~\ref{fig|scene}).

\subsection{Worlds}

Worlds are effectively distributed data structures composed of a scene graph
representing the 3D geometry of the environment, and a timeline storing temporal
events.

Each world is technically independent from every others. Dependencies between
worlds arise from the clients' connections. For instance, filters effectively
create a dependency between worlds. A client like the \textit{Physics-based
position correction} client create a dependency between the world {\tt base} (which
represents here the result of raw sensor fusion) and the world {\tt corrected}
which would be a physically-consistent copy of {\tt base}.

As a result, a \uwds network can be seen as a dependency graph (where
cyclic dependencies are permissible), and we call the whole architecture a
\emph{cascading situation assessment} system.

\subsubsection{Scenes}

@@

@@

\subsection{Standard Clients}
\label{std_clients}

@@

@@

\section{Application Example}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{}
    \label{}
\end{figure}
\uwds has been used within the European L2TOR project to...

...context + picture

...needs for spatial representation

\subsection*{Architecture}

...diagram with the various \uwds clients
